### 2018-12-18 Sections/models_for_quantum_computation.tex
reference added for adiabatic QC, need proof reading

\begin{align}
i \frac{\partial \ket{\psi(t)}}{\partial t} = H(t)\ket{\psi(t)}
\end{align}
\noindent will keep approximately to the instantaneous ground state, if $H(t)$ varies ``sufficiently slowly".

@@

\emph{The adiabatic quantum Grover algorithm} - as its name suggest, this is the adiabatic version of Grover's search algorithm \cite{}. The initial Hamiltonian is $H_0 = \openone - \ket{\phi}\bra{\phi}$, where $\ket{\phi}$ is the univorm superposition state $ \ket{+}^{\otimes n}. $
The final Hamiltonian is given by $H_1 = \openone - \ket{m}\bra{m}$, where $ \ket{m}$ is the marked item we are searching for.

\emph{Adiabatic Deutsch-Joza algorithm} - Given a function $f:\{0,1 \}^n \rightarrow {0,1}$ which is either constant or balanced, the Deutsch-Joza algorithm \cite{} can determine which type of function it is with a quantum speedup.

\emph{The glued-trees problem} Consider two binary trees each of depth $n$. Each tree has $2^{n+1}-1$ vertices, the two trees are randomly glued as in Fig~\ref{fig:glued_tree}). More specifically, a leaf is chosen from the left, is connected to a leaf on the right at random, which is then connected to another leaf on the left, and so on. Every leaf on the left is connected to two on the right and vice versa. This creats a random cycle that alternates between the two trees. The problem is to, starting from the left root, to find a path to the right root in the smallest possible number of steps. Classical algorithms require at least a subexponential in $n$ number of quiries, but there exists a polynomial-time quantum algorithm based on quantum walks.

\emph{Adiabatic PAGERANK algorithm} - the PAGERANK vector is a crucial tool in data mining and information retrival, used by the Google search engine. The current algorithm outperforms all known current classical algorithms by a polynomial or even exponential speedup, but better future classical algorithms have not been ruled out.

\begin{figure}[!htbp]
	\includegraphics[clip=true, width=0.5\textwidth]{glued_tree.pdf}
	\captionspacefig \caption{A glued tree with $n=4$} \label{fig:glued_tree}
\end{figure}

@@

It has been proven that AQC can efficiently simulate the circuit model \cite{}, which means that it is universal for quantum computing.

>>>>

\begin{align}
i \frac{\partial \ket{\psi(t)}}{\partial t} = H(t)\ket{\psi(t)}
\end{align}
\noindent will keep approximately to the instantaneous ground state, if $H(t)$ varies sufficiently slowly.

@@

\emph{The adiabatic quantum Grover algorithm} - as its name suggest, this is the adiabatic version of Grover's search algorithm. The initial Hamiltonian is $H_0 = \openone - \ket{\phi}\bra{\phi}$, where $\ket{\phi}$ is the univorm superposition state $ \ket{+}^{\otimes n}. $
The final Hamiltonian is given by $H_1 = \openone - \ket{m}\bra{m}$, where $ \ket{m}$ is the marked item we are searching for \cite{PhysRevA.65.042308}.

\emph{Adiabatic Deutsch-Joza algorithm} - Given a function $f:\{0,1 \}^n \rightarrow \{0,1\}$ which is either constant or balanced, the Deutsch-Joza algorithm can determine which type of function it is with a quantum speedup. An adiabatic implementation \cite{PhysRevLett.95.250503} is derived to match the speedup obtained as in the circuit model.

\emph{The glued-trees problem} - here we consider two binary trees each of depth $n$. Each tree has $2^{n+1}-1$ vertices, the two trees are randomly glued as in Fig~\ref{fig:glued_tree}. More specifically, a leaf is chosen from the left, is connected to a leaf on the right at random, which is then connected to another leaf on the left, and so on. Every leaf on the left is connected to two on the right and vice versa. This creats a random cycle that alternates between the two trees. The problem is to, starting from the left root, to find a path to the right root in the smallest possible number of steps. Classical algorithms require at least a subexponential in $n$ number of quiries, but there exists a polynomial-time quantum algorithm based on quantum walks \cite{childs2003exponential}.

\emph{Adiabatic PAGERANK algorithm} - the PAGERANK vector is a crucial tool in data mining and information retrival, used by the Google search engine. The current algorithm outperforms all known current classical algorithms by a polynomial or even exponential speedup \cite{PhysRevLett.108.230506}, but better future classical algorithms have not been ruled out.

\begin{figure}[!htbp]
	\includegraphics[trim = 0 0 0 1.3cm, clip=true, width=0.5\textwidth]{glued_tree.pdf}
	\captionspacefig \caption{A glued tree with $n=4$} \label{fig:glued_tree}
\end{figure}

@@

It has been proven that AQC can efficiently simulate the circuit model \cite{RevModPhys.90.015002}, which means that it is universal for quantum computing.
